Figures

### 2019-04-18 code/figures.rmd
Combined all Figure 3 versions into one figure using cowplot

#Plots of H2 and I2 vs. biserial correlation r for all effects together

I2 <- ggplot(res2, aes(x = r, y = I2)) +
  geom_point(alpha = 0.5) +
  geom_smooth(method = "lm", se = TRUE, color = "black") +
  coord_cartesian(ylim = c(0, 100)) +
  geom_text(x = 0.14, y = Inf, vjust = 7, fontface = "italic", size = 3.5, label = paste0("b = ", format(round(I2_fit$coefficients[2, 1], 2), nsmall = 2), ", r = ", format(round(sqrt(I2_fit$r.squared), 2), nsmall = 2))) +
  theme_classic() +
  scale_y_continuous(name = expression(paste(italic(I)^2," index"))) +
  scale_x_continuous(name = expression(paste("Biserial and pearson correlations ")))

H2 <- ggplot(res2, aes(x = r, y = H2)) + 
  geom_point(alpha = 0.5) +
  geom_smooth(method = "lm", se = TRUE, color = "black") +
  geom_text(x = 0.14, y = Inf, vjust = 7, size = 3.5, fontface = "italic", label = paste("b = ", format(round(H2_fit$coefficients[2, 1], 2), nsmall = 2), ", r = ", format(round(sqrt(H2_fit$r.squared), 2), nsmall = 2))) +
  theme_classic() +
  scale_y_continuous(name = expression(paste(italic(H)^2," index", sep = ""))) +
  scale_x_continuous(name = expression(paste("Biserial and pearson correlations ")))

effect_het <- plot_grid(I2, H2, nrow = 2, labels = c("a", "b"), align = "v") #combine plots
effect_het
#save_plot("../figures/effect-het.png", effect_het,
#          nrow = 2, base_height = 5, base_width = 5, dpi = 600)

##Alternative/additional Figure 3
```{r r_vs_tau2, fig.asp = 0.618, cache = TRUE}
r_tau2 <- ggplot(res2, aes(x = r, y = tau2)) + 
  geom_point(alpha = 0.5) +
  geom_smooth(method = "lm", se = TRUE, color = "black") +
  geom_text(x = 0.14, y = Inf, vjust = 7, size = 3.5, fontface = "italic", label = paste("b = ", format(round(tau2_fit$coefficients[2, 1], 2), nsmall = 2), ", r = ", format(round(sqrt(tau2_fit$r.squared), 2), nsmall = 2))) +
  theme_classic() +
  scale_y_continuous(name = expression(paste("Between studies variance ", italic(tau)^2))) +
  scale_x_continuous(name = expression(paste("Biserial and pearson correlations ")))

r_tau2 
# ggsave("../figures/r_tau2.png", dpi = 600, height =  4 , width = 6.47)

>>>>

#Plots of H2 and I2 vs. biserial correlation r for all effects together, two above chunks need to be run first

I2 <- ggplot(res2, aes(x = r, y = I2)) +
  geom_point(alpha = 0.5) +
  geom_smooth(method = "lm", se = TRUE, color = "black") +
  coord_cartesian(ylim = c(0, 100)) +
  annotate("text", x = 0.14, y = Inf, vjust = 5, fontface = "italic", size = 3.5, label = paste0("b = ", format(round(I2_fit$coefficients[2, 1], 2), nsmall = 2), ", r = ", format(round(sqrt(I2_fit$r.squared), 2), nsmall = 2))) +
  theme_classic() +
  theme(axis.text.x = element_blank(), #drop x-axis labels in preparation for combining plots
        axis.ticks.x = element_blank(),
        panel.border = element_rect(fill = NA, colour = "black", #add box around plots
                                    size = 0.5, linetype = "solid")) +
  scale_y_continuous(name = expression(paste(italic(I)^2," index"))) +
  scale_x_continuous(name = NULL)

H2 <- ggplot(res2, aes(x = r, y = H2)) + 
  geom_point(alpha = 0.5) +
  geom_smooth(method = "lm", se = TRUE, color = "black") +
  annotate("text", x = 0.14, y = Inf, vjust = 5, size = 3.5, fontface = "italic", label = paste("b = ", format(round(H2_fit$coefficients[2, 1], 2), nsmall = 2), ", r = ", format(round(sqrt(H2_fit$r.squared), 2), nsmall = 2))) +
  theme_classic() +
  theme(axis.text.x = element_blank(), #drop x-axis labels in preparation for combining plots
        axis.ticks.x = element_blank(),
        panel.border = element_rect(fill = NA, colour = "black", #add box around plots
                                    size = 0.5, linetype = "solid")) +
  scale_y_continuous(name = expression(paste(italic(H)^2," index", sep = ""))) +
  scale_x_continuous(name = NULL)

tau2 <- ggplot(res2, aes(x = r, y = tau2)) + 
  geom_point(alpha = 0.5) +
  geom_smooth(method = "lm", se = TRUE, color = "black") +
  annotate("text", x = 0.14, y = Inf, vjust = 5, size = 3.5, fontface = "italic", label = paste("b = ", format(round(tau2_fit$coefficients[2, 1], 2), nsmall = 2), ", r = ", format(round(sqrt(tau2_fit$r.squared), 2), nsmall = 2))) +
  theme_classic() +
  theme(panel.border = element_rect(fill = NA, colour = "black", #add box around plots
                                    size = 0.5, linetype = "solid")) +
  scale_y_continuous(name = expression(paste("Between studies variance ", italic(tau)^2))) +
  scale_x_continuous(name = expression(paste("Biserial and Pearson's correlations ")))

effect_het <- plot_grid(I2, H2, tau2, ncol = 1, align = "v", rel_heights = c(0.86, 0.86, 1)) #combine plots
effect_het
#save_plot("../figures/effect-het.png", effect_het,
#          ncol = 1, base_height = 7, base_width = 5, dpi = 600)
